Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
update of Simona's change

\documentclass[useAMS,usenatbib]{mn2e}
%\documentclass[usenatbib]{mn2e}
\usepackage{graphicx}
%\usepackage[nottoc]{tocbibind}

@@

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane. [NEED REF]  This is the famous ``missing
satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
understand this discrepancy, it is imperative to build up a large
sample of satellites/subhaloes in galaxies outside the Local Group.
This process is challenging due to the faintness of the satellite
galaxies.  Furthermore, lower-mass satellites may not be able to
retain the gas needed for ongoing star formation \citep[e.g.,][]{P11},
rendering them effectively dark.  These factors make gravitational
lensing a powerful and promising tool for the detection of
substructure.

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems \citep{Bradac02}. 
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction.  This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citet{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure. 
%
An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein ring
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

While future large-scale surveys, such as the LSST, are expected to
deliver new large samples of gravitationally lensed quasars, in the
near future the discovery of new systems using narrow-line quasar
emission \citep{N14} will provide new invaluable statistical
perspective on current constraints based on flux ratio anomalies.  In
this paper, we explore the idea that not all flux ratio anomalies are
related to the presence of substructure, but that some originate in a
more complex lens galaxy mass distribution than initially
considered. To this end we use new infra-red data from the Strong
lensing at High Angular Resolution Program (SHARP; Fassnacht et al.,
in prep). The main goal of the SHARP project is to re-observe known
quadruple and Einstein ring lens systems at a much higher angular
resolution by making use of observations with (1) adaptive optics (AO)
on the Keck telescopes, (2) the Hubble Space Telescope, and (3) large
interferometric arrays \citep{SHARP12,V12}. In particular, to better
understand the causes of flux ratio anomalies in gravitational lenses
we focus on the B1555+375 lens system\citep{Marlow99}.  This system was
discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
has a pair of merging images that show a strong flux ratio anomaly at
radio wavelengths.  Follow-up observations ruled out radio propagation
effects as the cause of the anomaly \citep{K03,KD04}.  The B1555+375
system was included in both the observational and theoretical analysis
of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
mass distribution is of key importantce.  Our analysis makes use of
the new information obtained from the latest SHARP infrared imaging.
The paper is organized as follows: the latest SHARP data are
introduced in section 2; in section 3 we present the lens model while
the results of this analysis and their implications are discussed in
section 4.

%However, only small number of flux ratio anomalous systems in \simona{the} radio are \simona{currently} avaliable. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach \simona{is to} seek out more flux ratio anomalous systems \simona{using} narrow-line quasar emission \citep{N14}. 
%	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems. \citet{V09, H13} both analyze the strong lens imaging to detect substructures lie infront of Einstein ring. Their methods improve the detectable mass limit and also show that high spatial resolution imaging is essential for the substructure study. On the other hand, numerical simulations on structure formation do not reach the concise conclusion on flux ratio anomalous systems. The latest study on the cause of flux anomalies from \citet{Xu14} shows the low probability of the existence of substructures in their studied systems. 
%	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. 
%To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging. We present the latest SHARP data in part 2, lens model of B1555+375 in part 3, and discussion in part 4.

@@

As a first trail of modelling, we create a single SIE model to 
justify the perforamnce of a simple lensing potential. Consistent with previous studies
\citep{Marlow99, Xu14}, our single elliptical potential model cannot predict flux anomaly in B1555+375. 
We then create two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =1.5$. Our steps to explore the parameter space are: 1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{Marlow99} as the start point of the bulge component and the source position. 2) Let all parameters without priors vary to reach a temporary best-fit. 3) Start with the best-fit in step 2 and let all parameters with priors vary to reach another best-fit (also ensure this best-fit is not far from the priors). 4) Let all parameters vary to reach the final optimal model. 
The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.
[WHY NO EXTERNAL SHEAR?---WITH ONLY THE RADIO POSITIONS AND FLUXES AS
CONSTRAINTS, ADDING SHEAR WOULD MAKE THE PROBLEM EVEN MORE UNDERCONSTRAINED]

[WHERE DO WE PUT MODEL CHI-SQUARE??]

@@

Comparision between radio and model-predicted lensed image positions. Observation data quoted from Table 2 in \citet{Marlow99}. Position offsets are in unit of arcsec. Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.

@@

Gravitational lensing is [one of] the most powerful methods for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes.  It is
for this reason that much of the effort in the flux-ratio technique
has been focused on radio-loud lens systems.  At these wavelengths,
dust extinction and microlensing effects should be minimal
\citep[although see][for a rare example of radio microlensing]{K2000}.
Radio propagation effects can affect radio fluxes, as is clearly shown
in the B0128+437 system \citep{B04}.  However, these propagation
effects can be disentangled from substructure lensing because they
have well known dependencies on wavelength. \citet{KD04} examine all
eight radio loud flux anomalous lenses besides B0128=437, namely: MG
0414+0534, B0712+472, B1359+154, B1422+231, B1555+375, B1608+656,
B1933+503, and B2045+265.  They find no strong wavelength dependence
in the flux ratios of all these systems and therefore rule out radio
propagation effects as significant contributors to the observed
anomalies.

In our models based on the new imaging from the SHARP $K^{\prime}$
band observations, the most significant difference in comparison to
previous modelling is a new edge-on disk component. With a bulge plus
an edge-on disk, our models produce matches to both the radio image
positions and the flux ratio, while models with only one SIE
component \citep{Marlow99,Xu14} fail to reproduce the fluxes
correctly. Our successful modelling indicates that the
kiloparsec-scale structure of lens galaxy itself is sufficient to
explain the flux ratio anomalies in B1555+375, without any need to
invoke the presense of substructure.

% This breaks the idea that in strongly lensed quasars, radio flux ratio
% anomalies are most likely originated from substructure
% perturbations. Our discovery shows a complex lens galaxy mass
% distribution can dominate flux ratio anomalous phenomena in a strongly
% lensed system.

@@

Additional near-infrared AO imaging from SHARP shows that B1555+375 is
not the only system having a significant disk component detection in
the lensing galaxy (see Fig 4).  These systems will be investigated in
future work, but the images alone strongly suggest that other lens
systems have similar links between flux-ratio anomalies and disk
components.  Although the number of radio loud flux anomalous lensed
quasars remains small, a new technique using narrow-line emission
regions will enlarge the sample and bring statistical perspective on
substructures in the near future \citep{N14}. It is well known (e.g,
Kochanek 199??) that lens models based only on the locations of lensed
quasar/AGN images have large degeneracies.  Therefore, before
concluding that the flux ratios in any given lens system are a result
of substructure, it is critical to explore a range of smooth models
that are informed by additional observations or to do a comprehensive
analysis such as that conducted by \citet{Xu14}.  Otherwise, derived
substructure fractions should be considered as upper limits.

% We would like to draw attention to the possible impacts on
% substructure searching from this enge-on disk orginated flux
% anomalies. It is a sign that researchers should be careful about the
% flux anomalies fraction in lensed quasars. It may be worth considering
% an upper limit of flux anomalies fraciton from observation results to
% avoid over estimate the number of substructure detections. For further
% analysis on substurcture population, mass function etc., it is always
% important to rule out other non-substructure effects.

[PERHAPS REARRANGE THE FOLLOWING INTO A CONCLUSIONS SECTION??]

In this paper we also demostrate the power of combining multiwavelength high resolution data. All the flux anomalous lensed quasars are radio loud systems and are first discovered in radio observations. Radio data provides reliable information on positions and fluxes of lensed images but often unable to detect lens galaxies. Since lens galaxies are mostly in low redshift, optical and near-infrared observations are ideal to measure the light distribution of lens gaxies and obtain prior on underlying mass distribution. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling. The improvement is even more dramatic in B1555+375. With HST and SHARP AO high resolution imaging, we detect an edge-on disk which does not appear in any previous discussions on B1555+375. This new discovered edge-on disk provides a strong prior for our lens modelling and we show that it adequately explain sthe flux ratio anomaly in B1555+375. Our results demostrate that lack of knowledge of lens galaxies can lead to improper lens models. Modelling with only four image positions from radio data can also cause a lot of degeneracy. With the first system analyzing and finding an edge-on disk originated flux ratio anomaly, our follow up will be explore other similar SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. An edge-on disk structure may also be able to expalin the flux ratio anomalies of these systems.

%From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g. include an exponential disk), rather than just assuming smooth potential. Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. If the non-substructure effect from edge-on disks does not included, expected ``false'' substructure detections can serverly bias the data analysis. Even with real substructures presence, the lens galaxy structure can still dominate flux anomalous phenomena. For precise measurements on substurcture population, mass function, and any derived properties from strongly lensed flux anomalous systems, it is crucial to have careful estimation on non-substructure effects. We would like to draw attention to this edge-on disk orginated flux anomalies due to its impacts on substructure searching.

\section*{Acknowledgments}

\bibliographystyle{mn2e}
\bibliography{reference.bib}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
%\documentclass[usenatbib]{mn2e}
\usepackage{graphicx}
%\usepackage[nottoc]{tocbibind}
\setlength{\topmargin}{-1.2cm}

@@

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane {\bf and the latest discovery of new dwarf galaxies}. [NEED REF]  
This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
understand this discrepancy, it is imperative to build up a large
sample of satellites/subhaloes in galaxies outside the Local Group.
{\bf However,} this process is challenging due to the faintness of the satellite
galaxies.  Furthermore, lower-mass satellites may not be able to
retain the gas needed for ongoing star formation \citep[e.g.,][]{P11},
rendering them effectively dark.  These factors make gravitational
lensing a powerful and promising tool for the detection of
substructure.

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems \citep{Bradac02}. 
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction. This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citet{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure. 
%
An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

While future large-scale surveys, such as the LSST, are expected to
deliver new large samples of gravitationally lensed quasars, in the
near future the discovery of new systems using narrow-line quasar
emission \citep{N14} will provide new invaluable statistical
perspective on current constraints based on flux ratio anomalies.  In
this {\bf letter}, we explore the idea that not all flux ratio anomalies are
related to the presence of substructure, but that some originate in a
more complex lens galaxy mass distribution than initially
considered. To this end we use new infra-red data from the Strong
lensing at High Angular Resolution Program (SHARP; Fassnacht et al.,
in prep). The main goal of the SHARP project is to re-observe known
quadruple and Einstein ring lens systems at a much higher angular
resolution by making use of observations with (1) adaptive optics (AO)
on the Keck telescopes, (2) the Hubble Space Telescope, and (3) large
interferometric arrays \citep{SHARP12,V12}. In particular, to better
understand the causes of flux ratio anomalies in gravitational lenses
we focus on the B1555+375 lens system\citep{Marlow99}.  This system was
discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
has a pair of merging images that show a strong flux ratio anomaly at
radio wavelengths.  Follow-up observations ruled out radio propagation
effects as the cause of the anomaly \citep{K03,KD04}.  The B1555+375
system was included in both the observational and theoretical analysis
of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
mass distribution is of key importance.  Our analysis makes use of
the new information obtained from the latest SHARP infrared imaging.
The paper is organized as follows: the latest SHARP data are
introduced in section 2; in section 3 we present the lens model while
the results of this analysis and their implications are discussed in
section 4.

@@

As a first trail of modelling, we create a single SIE model to 
justify the performance of a simple lensing potential. Consistent with previous studies
\citep{Marlow99, Xu14}, our single elliptical potential model cannot predict flux anomaly in B1555+375. 
We then create two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =1.5$. Our steps to explore the parameter space are: 1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{Marlow99} as the start point of the bulge component and the source position. 2) Let all parameters without priors vary to reach a temporary best-fit. 3) Start with the best-fit in step 2 and let all parameters with priors vary to reach another best-fit (also ensure this best-fit is not far from the priors). 4) Let all parameters vary to reach the final optimal model. 
The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.
{\bf We have not included an external shear component into our model because the constraints provided by the image positions and  fluxes would not be sufficient 
to constrain such a model. However, we note that the image not affected by dust (image C) in the Keck AO data is consistent with negligible shear (i.e. shear strength $\Gamma_s=0.002$), when modelled with the pixelized technique by \citet{V09}.}

@@

Comparison between radio and model-predicted lensed image positions. Observation data quoted from Table 2 in \citet{Marlow99}. Position offsets are in unit of arcsec. Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.

@@

Gravitational lensing is, {\bf at present,} the most powerful tool for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes{\bf, such as propagation effects and assumptions on the mass distribution of the lens galaxy}.  
It is for this reason that much of the effort in the flux-ratio technique
has been focused on radio-loud lens systems.  At these wavelengths,
dust extinction and microlensing effects should be minimal
\citep[although see][for a rare example of radio microlensing]{K2000}.
Radio propagation effects can affect radio fluxes, as is clearly shown
in the B0128+437 system \citep{B04}.  However, these propagation
effects can be disentangled from substructure lensing because they
have well known dependencies on wavelength. \citet{KD04} examine all
eight radio loud flux anomalous lenses besides B0128=437, namely: MG
0414+0534, B0712+472, B1359+154, B1422+231, B1555+375, B1608+656,
B1933+503, and B2045+265.  They find no strong wavelength dependence
in the flux ratios of all these systems and therefore rule out radio
propagation effects as significant contributors to the observed
anomalies.

{\bf In this letter, we focus on the effect of more complicated mass distributions for the lens galaxy on flux ratio anomalies.
Traditionally, flux anomalous lensed quasars are radio loud systems that are firstly discovered in radio observations. While radio data provide reliable information on the positions and the fluxes of the lensed images, they are often unable to detect the lens galaxies. Moreover, lens modelling based only on the positions of the four images can be highly degenerate and prior assumptions play a key role in the interpretation of the observed flux ratio anomaly.
Since lens galaxies are mostly located at low redshift, optical and near-infrared observations are ideal to measure the light distribution of lens galaxies and obtain useful prior information  
on the underlying mass distribution. Indeed \citet{SHARP12} has shown that high resolution IR imaging can help to significantly improve the precision of the lens modelling. This improvement is even more dramatic in the case of B1555+375, where HST and SHARP AO high resolution imaging, has allowed us to detect, for the fist time, the presence of an edge-on disk. This new discovered edge-on disk provides a strong prior for our lens modelling.  With a bulge plus an edge-on disk, our models produce matches to both the radio image
positions and their flux ratio, while models with only one SIE component \citep{Marlow99,Xu14} fail to reproduce the fluxes correctly. Our successful modelling indicates that the
kiloparsec-scale structure of the lens galaxy itself is sufficient to explain the flux ratio anomalies in B1555+375, without any need to invoke the presence of substructure.  }

@@

Additional near-infrared AO imaging from SHARP shows that B1555+375 is
not the only system having a significant disk component detection in
the lensing galaxy.  These systems will be investigated in
future work, but the images alone strongly suggest that other lens
systems have similar links between flux-ratio anomalies and disk
components.  Although the number of radio loud flux anomalous lensed
quasars remains small, a new technique using narrow-line emission
regions will enlarge the sample and bring statistical perspective on
substructures in the near future \citep{N14}. It is well known (e.g,
Kochanek 199??) that lens models based only on the locations of lensed
quasar/AGN images have large degeneracies. Therefore, before
concluding that the flux ratios in any given lens system are a result
of substructure, it is critical to explore a range of smooth models
that are informed by additional observations or to do a comprehensive
analysis such as that conducted by \citet{Xu14}. Otherwise, derived
substructure fractions should be considered as upper limits.

\section{Conclusions}
{\bf In this letter we have taken advantage of the power of multi-wavelength high resolution data to investigate whether flux ratio anomalies could be explained by more complex smooth models for the lens galaxy mass distribution rather than substructure. Thanks to new imaging from the SHARP $K^{\prime}$ band observations of the gravitational lens system B1555+375 we have identified the existence of a previously undetected edge-on disk. By including this disk in the mass model of the lens galaxy we find a good fit for both the positions and flux ratios of the lensed images. Our results clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of a few lensed images, can lead to improper lens models and a misinterpretation of the origin of flux ratio anomalies. 
We stress, therefore, that one should be very careful when interpreting the nature of flux ratio anomalies, as prior assumptions on the lens mass distribution are a significant source of bias. Finally, our analysis shows that in order to derive precise quantification of the substructure population and any derived properties from strongly lensed flux anomalous systems, it is crucial to have a careful estimation of non-substructure effects. In fact, even in the presence of mass substructures, the observed flux ratio anomalies could be still dominated by the complex structure of the lens galaxy.}

%. Modelling with only four image positions from radio data can also cause a lot of degeneracy. With the first system analyzing and finding an edge-on disk originated flux ratio anomaly, our follow up will be explore other similar SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. An edge-on disk structure may also be able to explain the flux ratio anomalies of these systems.
 %From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g. include an exponential disk), rather than just assuming smooth potential. Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. If the non-substructure effect from edge-on disks does not included, expected ``false'' substructure detections can serverly bias the data analysis. 
% This breaks the idea that in strongly lensed quasars, radio flux ratio
% anomalies are most likely originated from substructure
% perturbations. Our discovery shows a complex lens galaxy mass
% distribution can dominate flux ratio anomalous phenomena in a strongly
% lensed system.
% We would like to draw attention to the possible impacts on
% substructure searching from this enge-on disk orginated flux
% anomalies. It is a sign that researchers should be careful about the
% flux anomalies fraction in lensed quasars. It may be worth considering
% an upper limit of flux anomalies fraciton from observation results to
% avoid over estimate the number of substructure detections. For further
% analysis on substurcture population, mass function etc., it is always
% important to rule out other non-substructure effects.

\section*{Acknowledgments}
S.V. is grateful to Dandan Xu for useful discussion on the nature of flux ratio anomalies in high resolution numerical simulations.
\bibliographystyle{mn2e}
\bibliography{reference.bib}
